Draft_Application_Stochastic_Volatility

### 2021-07-16 Real Dataset SV.Rmd
introduction

output:
  pdf_document: 
   latex_engine: xelatex
   fig_width: 5
   fig_height: 3.5
   fig_caption: true
   extra_dependencies: ["float"]
   number_sections: true 
---

@@

As regards the series that we will employ in section (\textit{fill with the number of the section}), namely the series of realised volatilities which we will employ as a proxy for the true latent volatilities, the data were retrieved from the Oxford-Man Institute's Realized Library, which provides several different daily non-parametric measures of past volatility. We consider a proper rescaling of the \textit{rv5} series, \textit{i.e.} model-free daily volatility estimates based on 5 min intraday return intervals. Also in this case, the chosen interval spanned from June 1st, 2017 to May 30th, 2021.

>>>>

output:
  pdf_document: 
   latex_engine: xelatex
   fig_width: 5
   fig_height: 3.5
   fig_caption: true
   extra_dependencies: ["float"]
   number_sections: true 
---
\section{Overview}
In the following sections, we will try to replicate some of the analyses which were previously conducted on synthetic data, generated by a basic stochastic volatility model; this time, the same model specification and filters will be used on real data. However, as we will see, real data require different strategies to evaluate the effectiveness of several Sequential Monte Carlo techniques. Intuitively, such differences are due to the fact that now the latent process driving the Hidden Markov Model is not observed, nor do we know exactly its law of motion. 
This part of the work is structured as follows:

@@

As regards the series that we will employ in section (\textit{fill with the number of the section}), namely the series of realised volatilities which we will employ as a proxy for the true latent volatilities, the data were retrieved from the Oxford-Man Institute's Realized Library, which provides several different daily non-parametric measures of past volatility. We consider a proper rescaling of the \textit{rv5} series, \textit{i.e.} model-free daily volatility estimates based on 5 min intraday return intervals. Also in this case, the chosen interval spanned from June 1st, 2017 to May 30th, 2021. \textit{Includere grafico e commento del grafico della realised volatility}
